Changelog

### 2021-05-25 Chapter-1/Chapter-1.tex
Updates from Overleaf

\begin{enumerate}
    \item It is hard to identify side-channel vulnerabilities in real-world software. In general, many side-channel vulnerabilities are low-level problems. Control-flows or memory accesses may not be side-channel vulnerabilities if they are independent of the secret inputs. Recent work can identify side-channel leakages. But those tools can only work on small programs or need to apply domain knowledge of the target program to simplify the analysis.
    \item Side-channel vulnerabilities are ubiquitous. While some vulnerabilities can result in the key being entirely compromised, many other vulnerabilities are hard to exploit. Moreover, some vulnerable implementations perform better. Recent work can identify thousands of leaked points, but most of them are not patched by developers because those leakages are either false positives or leaked very little information.
\end{enumerate}

>>>>

\begin{enumerate}
    \item It is hard to identify side-channel vulnerabilities in real-world software. In general, many side-channel vulnerabilities are low-level problems. Control-flows or memory accesses may not be side-channel vulnerabilities if they are independent of the secret inputs. Recent work can identify side-channel leakages. But these tools can only work on small programs or need to apply domain knowledge of the target program to simplify the analysis.
    \item Side-channel vulnerabilities are ubiquitous. While some vulnerabilities can result in the key being entirely compromised, many other vulnerabilities are hard to exploit. Moreover, some vulnerable implementations perform better. Recent work can identify thousands of leaked points, but most of them are not patched by developers because these leakages are either false positives or leaked very little information.
\end{enumerate}

### 2021-05-25 Chapter-6/Chapter-6.tex
Updates from Overleaf

\textbf{Leakages.} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort. After we manually analyze those leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages. 
\section{Precise Analysis on Single-trace Attacks}
While recent work found many side-channel vulnerabilities,
we note that many of them have not been patched by developers.
Side-channels are ubiquitous in software and it would be difficult to fix all of them.
We need a tool that estimates the sensitivity of each vulnerability
so software engineers can focus on
``severe'' leakages. For example, \tool{} reports that
the modular exponentiation using square and multiply algorithms can
leak more information than a key validation function.

@@

\tool{} reaches full precision if the number of estimated leaked bits
equals to Definition~\ref{chapter4:def}.
\tool{} may lose precision from the
memory model it uses in theory. However, we did not find false positives
caused by the imprecise memory model during our evaluation.
Sampling introduces imprecision but with a probabilistic guarantee.
However, during the evaluation, we find that \tool{} cannot estimate
the amount of leakage for some leakage sites in a reasonable time,
which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def}, it means the leakage is very severe. 
\section{Precise Analysis on Multiple-trace Attacks}
This paper presents an approach that tries to give a conservative
estimate of the amount of leaked information by address-based
side-channel attacks. Those attacks exploit the data-flow from secrets
to load address and the data-flow from the data-flow from secrets to
branch conditions to retrieve secrets based on the observation on the
memory accesses. Although those kinds of side-channel leakages have
been discovered for decades, the up-to-date software still has some
side-channel leakages. For some of those vulnerabilities, developers
do not fix them because they think those side-channel vulnerabilities
are not important. To show the importance of those side-channel
leakages, one way is to demonstrate an end-to-end attack based on the
vulnerability. However, demonstrating an end-to-end attack often need
a lot of manual effort and the domain knowledge of the victim program,
which is not often the case in practice. It is good to have a tool
that automatically assesses the severity level of those side-channel
leakages. So it would be better to have a proper metric to quantify
the side-channel leakage. However, we find previous side-channel
quantification tools are developed to ensure the noninterference of
the program. They use the over-approximation heuristics method to
quantify the leakage. For example, CacheAudit estimates that a 128-bit
AES encryption can leak more than 128 bits. As a result, even those
tools report severe leakage, it does not mean the program has a truly
severe leakage.

@@

\ctool{} is a dynamic approach. So it bears the same limitations of dynamic approaches as well. \ctool{} may have the coverage problem and can miss some side-channel vulnerabilities. It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control flow under various inputs. For other libraries like graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities. However, \ctool{} is not designed to find side-channel vulnerabilities. The goal of \ctool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities. So we do not think it is the main limitation of \ctool{}. However, users of \ctool{} should be aware of the code coverage problem.

\section{Limitations}

>>>>

\textbf{Leakages.} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort. After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages. 
\section{Precise Analysis on Single-trace Attacks}
While recent work found many side-channel vulnerabilities,
we note that many of them have not been patched by developers.
Side-channels are ubiquitous in software and it would be difficult to fix all of them.
We need a tool that estimates the sensitivity of each vulnerability
so software engineers can focus on
``severe'' leakages. For example, \tool{} reports that
the modular exponentiation using square and multiply algorithms can
leak more information than a key validation function.

@@

\tool{} reaches full precision if the number of estimated leaked bits
equals to Definition~\ref{chapter4:def}.
\tool{} may lose precision from the
memory model it uses in theory. However, we did not find false positives
caused by the imprecise memory model during our evaluation.
Sampling introduces imprecision but with a probabilistic guarantee.
However, during the evaluation, we find that \tool{} cannot estimate
the amount of leakage for some leakage sites in a reasonable time,
which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def}, it means the leakage is very severe. 
\section{Precise Analysis on Multiple-trace Attacks}
This paper presents an approach that tries to give a conservative
estimate of the amount of leaked information by address-based
side-channel attacks. These attacks exploit the data-flow from secrets
to load address and the data-flow from the data-flow from secrets to
branch conditions to retrieve secrets based on the observation on the
memory accesses. Although these kinds of side-channel leakages have
been discovered for decades, the up-to-date software still has some
side-channel leakages. For some of these vulnerabilities, developers
do not fix them because they think these side-channel vulnerabilities
are not important. To show the importance of these side-channel
leakages, one way is to demonstrate an end-to-end attack based on the
vulnerability. However, demonstrating an end-to-end attack often need
a lot of manual effort and the domain knowledge of the victim program,
which is not often the case in practice. It is good to have a tool
that automatically assesses the severity level of these side-channel
leakages. So it would be better to have a proper metric to quantify
the side-channel leakage. However, we find previous side-channel
quantification tools are developed to ensure the noninterference of
the program. They use the over-approximation heuristics method to
quantify the leakage. For example, CacheAudit estimates that a 128-bit
AES encryption can leak more than 128 bits. As a result, even these
tools report severe leakage, it does not mean the program has a truly
severe leakage.

@@

\ctool{} is a dynamic approach. So it bears the same limitations of dynamic approaches as well. \ctool{} may have the coverage problem and can miss some side-channel vulnerabilities. It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control flow under various inputs. For other libraries such as graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities. However, \ctool{} is not designed to find side-channel vulnerabilities. The goal of \ctool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities. So we do not think it is the main limitation of \ctool{}. However, users of \ctool{} should be aware of the code coverage problem.
